An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-08-01 article.tex
fixed minor latex error with \degree

Observing Figure \ref{fig:yield_vs_value} shows an almost discrete difference between vineyards in 'Hot' areas than other regions. Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows almost opposing trends; a not so obvious difference between the Figures, is that the difference is mostly a rotation (being a $90^\degree$ clockwise reflection). However, with area coming into play, many data points are scaled differently; specifically the vineyards from 'Hot' regions are then found to be on the tail end, producing large quantity of lower value grapes. This is more visible when comparing both graphs to the map of regional averages for response variables, see Figure \ref{fig:map}. There is a notable change between regional averages when looking at yield verse value. Through the coefficients we can deduce that: this difference is also a difference between more resources used for the raw response variables; and a difference between overall resource use and the size of the vineyard. Where resource use and area harvested have a combined relationship through their interaction and separate relationships as individual variables (see Table \ref{tab:contvar}). A notable occurrence in Figure \ref{fig:yield_vs_value_area}, is that the 'Very Dry' vineyards which produce lower yields and higher quality grapes are predominantly found in the Barossa Valley (a wine region known for its high quality Shiraz). This note is important as it shows climate is not exclusively the consideration, soil and other geographical phenomenon have considerable impacts on vineyard outcomes.

>>>>

Observing Figure \ref{fig:yield_vs_value} shows an almost discrete difference between vineyards in 'Hot' areas than other regions. Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows almost opposing trends; a not so obvious difference between the Figures, is that the difference is mostly a rotation (being 90\textdegree clockwise). However, with area coming into play, many data points are scaled differently; specifically the vineyards from 'Hot' regions are then found to be on the tail end, producing large quantity of lower value grapes. This is more visible when comparing both graphs to the map of regional averages for response variables, see Figure \ref{fig:map}. There is a notable change between regional averages when looking at yield verse value. Through the coefficients we can deduce that: this difference is also a difference between more resources used for the raw response variables; and a difference between overall resource use and the size of the vineyard. Where resource use and area harvested have a combined relationship through their interaction and separate relationships as individual variables (see Table \ref{tab:contvar}). A notable occurrence in Figure \ref{fig:yield_vs_value_area}, is that the 'Very Dry' vineyards which produce lower yields and higher quality grapes are predominantly found in the Barossa Valley (a wine region known for its high quality Shiraz). This note is important as it shows climate is not exclusively the consideration, soil and other geographical phenomenon have considerable impacts on vineyard outcomes.
